NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-14 paper/Chapters/Chapter4.tex
before meeting Luigi at 14th August

For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate eating pattern people were switching between different types of carbohydrate consumptions. The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals. This properly accounted for the fact that for some people, their probability of following a regular meals day during the survey was much higher than the others (low carbohydrate eaters); and for some people, their probability of following high carbohydrate eating day during their survey were quite high (high carbohydrate eaters); while for the rest of the participants, they had similar probabilities of following either regular meals day or high carbohydrate eating day (moderate carbohydrate eaters).

>>>>

For the first time, as far as we know, the non-parametric MLCA models successfully captured the day-to-day variability within individuals as expected and showed that from the perspective of carbohydrate consumption people were switching between different types of carbohydrate consumptions. The MLCA models allowed the probability of a certain type of carbohydrate eating day to vary across individuals. This properly accounted for the fact that for some people, their probability of following a regular meals day during the survey was much higher than the others (low carbohydrate eaters); and for some people, their probability of following high carbohydrate eating day during their survey were quite high (high carbohydrate eaters); while for the rest of the participants, they had similar probabilities of following either regular meals day or high carbohydrate eating day (moderate carbohydrate eaters).

Surprisingly, low carbohydrate eaters turned out to consume the highest amount of total energy,
